Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-17 introduction.tex
Rearranging sections - cleaned this up a bit.

The structure of the code is as follows.  In Section~\ref{sec.overview}, we first provide a top-level overview of the code method and structure.  This is designed to give a first broad-brush picture of the equations we aim to solve and the methods used to solve them.  Next, in Section~\ref{sec.methods}, we describe the methods we use in detail, reserving some of the longer descriptions of particular components for the appendix in order not to interrupt the flow of the paper.  The \enzo\ testing framework and code tests are described in Section~\ref{sec.tests}.  The parallelism strategy and scaling results are described in Section~\ref{sec.parallel}.  Finally, we discuss the code's development methodology (which is as far as we know unique in the astrophysics community) in Section~\ref{sec.development}.

>>>>

The structure of the code is as follows.  In Section~\ref{sec.overview}, we first provide a top-level overview of the code method and structure.  This is designed to give a first broad-brush picture of the equations we aim to solve and the methods used to solve them.  Next, in Sections~\ref{sec.amr} through~\ref{sec.num.analysis}, we describe the methods we use in detail, reserving some of the longer descriptions of particular components for the appendix in order not to interrupt the flow of the paper.  The \enzo\ testing framework and code tests are described in Section~\ref{sec.tests}.  The parallelism strategy and scaling results are described in Section~\ref{sec.parallel}.  Finally, we discuss the code's development methodology (which is as far as we know unique in the astrophysics community) in Section~\ref{sec.development}.

### 2013-05-17 overview.tex
Adding AMR scaling section with an associated table.  I still need to add some references in this section.  Fixing some undefined and multiple labels and making the UVB table wider and spaced nicely.
Rearranging sections - cleaned this up a bit.

We begin this section by first writing down the complete set of
physical equations that be solved by \enzo, and then briefly describe
the numerical algorithms that we use to solve these equations.  This
section is intended to be an overview of the \enzo\ code's
capabilities: thus, we gather all of the equations solved into a
single place and provide a brief and high-level introduction to the
numerics of the code.  Detailed descriptions of the individual
components are then provided in Section~\ref{sec.methods}.

@@

In this section, we briefly describe the numerical methods which are
used to solve the equations outlined in Section~\ref{sec.equations}.  We
proceed through the numerical methods in the same order as will be used in
section~\ref{sec.methods} so that there is a one-to-one correspondence
between each of the following overviews and the complete description
provided in that section.  The goal here is to introduce the reader to
the basic principles of the methods without drowning in detail.

@@

\subsubsection{MHD with Constrained Transport (MHD)}
This MHD method is second order in time and space, and preserves the divergence constraint,
$\nabla \cdot \vecB = 0$, to machine precision through the Constrained Transport
(CT) method.  CT, originally described by \citet{Evans88}, updates the
magnetic field with the curl of an electric field, suitably formulated to
preserve $\nabla \cdot \vecB$.  We employ the CT methods
described by \citet{Balsara99} and \citet{Gardiner05}.  Further, we employ the
second order hyperbolic solver of \citet{Li08} and the divergence free AMR
scheme of \citet{Balsara01}.

>>>>

We begin this section by first writing down the complete set of
physical equations that be solved by \enzo, and then briefly describe
the numerical algorithms that we use to solve these equations.  This
section is intended to be an overview of the \enzo\ code's
capabilities: thus, we gather all of the equations solved into a
single place and provide a brief and high-level introduction to the
numerics of the code.  Detailed descriptions of the individual
components are then provided in Sections~\ref{sec.amr}-\ref{sec.num.analysis}.

@@

In this section, we briefly describe the numerical methods which are
used to solve the equations outlined in Section~\ref{sec.equations}.  We
proceed through the numerical methods in the same order as will be used in
Sections~\ref{sec.amr} through~\ref{sec.num.analysis} so that there is a one-to-one correspondence
between each of the following overviews and the complete description
provided in the later sections.  The goal in this section is to introduce the reader to
the basic principles of the methods without drowning in detail.

@@

\subsubsection{MHD with Constrained Transport (MHD)}
This MHD method is second order in time and space, and preserves the divergence constraint,
$\nabla \cdot \vecB = 0$, to machine precision through the Constrained Transport
(CT) method.  CT, originally described by \citet{Evans88}, updates the
magnetic field with the curl of an electric field, suitably formulated to
preserve $\nabla \cdot \vecB$.  We employ the CT methods
described by \citet{Balsara99} and \citet{Gardiner05}.  Further, we employ the
second order hyperbolic solver of \citet{Li08a} and the divergence free AMR
scheme of \citet{Balsara01}.
